14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-04 rules/rules19.tex
Rules: Use rm font for urls.
Rules: Remove todo.

@@

\begin{itemize}
\item SMT-COMP mailing list:
  \href{mailto:smt-comp@cs.nyu.edu}{\texttt{smt-comp@cs.nyu.edu}}
\item Sign-up site for the mailing list:
  \url{http://cs.nyu.edu/mailman/listinfo/smt-comp}
\end{itemize}

@@

The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
pair in the single problem, incremental and unsat core tracks, \rem{TODO:
XX}~minutes in the industry challenge track, and \rem{TODO: XX}~minutes in the
model validation track \an{TODO: Need to elaborate how time is split? Do we
need two time limits here, one for solving and one for
validation?}.\footnote{\an{TODO: Is this obsolete?} The time limit may be
adjusted once we know the number of competition entrants and eligible
benchmarks.}  Solvers that take more than this time limit will be killed.
Solvers are allowed to spawn other processes; these will be killed at
approximately the same time as the first started process.

>>>>

\urlstyle{same}

@@

\begin{itemize}
\item SMT-COMP mailing list:
  \href{mailto:smt-comp@cs.nyu.edu}{\textrm{smt-comp@cs.nyu.edu}}
\item Sign-up site for the mailing list:
  \url{http://cs.nyu.edu/mailman/listinfo/smt-comp}
\end{itemize}

@@

The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
pair in the single problem, incremental and unsat core tracks, \rem{TODO:
XX}~minutes in the industry challenge track, and \rem{TODO: XX}~minutes in the
model validation track \an{TODO: Need to elaborate how time is split? Do we
need two time limits here, one for solving and one for
validation?}.\footnote{The time limit may be
adjusted once we know the number of competition entrants and eligible
benchmarks.}  Solvers that take more than this time limit will be killed.
Solvers are allowed to spawn other processes; these will be killed at
approximately the same time as the first started process.
